Limited information strategies for a topological proximal game

### 2015-05-15 phd/talks-and-presentations/2015-05-13-topological-proximal-game.tex
final touches to conference talk

\subtitle
{Spring Topology Conference 2015} % (optional)

\author%[Author, Another] % (optional, use only with lots of authors)
{Steven~Clontz~http://stevenclontz.com}%\inst{1} \and S.~Another\inst{2}}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\begin{document}
% \renewcommand{\pause}{}
\newcommand{\vspacing}{\vspace{1em}}
\newcommand{\vpause}{\pause\vspacing}

@@

\section{Bell's Proximal Game}

@@

\begin{frame}
  If $\pl D\win \bellAbsConGame{X}$, then $X$ is called an
  \term{absolutely proximal space}.
  ``Absolutely proximal'' is a strengthening of ``proximal'', but these
  concepts coincide for (uniformlly locally) compact spaces.

@@

\section{Topologizing Bell's game}

@@

  As it turns out, the union of all uniformities inducing a topology is
  itself a uniformity inducing that topology, called the
  \term{universal uniformity}. Furthermore, $\pl D\win\bellAbsConGame{X}$
  if and only if $\pl D$ is required to choose from the universal uniformity.

@@

\begin{frame}
  From Willard's topology text \cite{MR2048350}, we have such
  a characterization:

  \begin{theorem}
    A neighborhood $U$ of the diagonal is a universal uniformity if
    and only if there
    exist neighborhoods $U_n$ for $n<\omega$ where $U=U_0$ and
    $U_{n+1}\circ U_{n+1}\subseteq U_n$.
  \end{theorem}

@@

  As a bonus, for strongly collectionwise normal
  ($\Leftarrow$ paracompact) spaces, \textit{all} neighborhoods of
  the diagonal have this property.

@@

  So we topologize Bell's game by
  saying an ``entourage'' is any (open symmetric) neighborhood of the
  diagonal with this property, and discard the need to consider a
  specific uniform structure.
\end{frame}

@@

  \vpause
  A \term{$k$-Markov strategy} only uses the round number and the last $k$
  previous moves of the opponent. ($\pl A\kmarkwin{k} G$)

@@

\begin{frame}\small
  Bell showed that a winning perfect information strategy may always
  be passed down to win in a closed subspace.

@@

  This actually holds in general:

@@

\begin{frame}
  We settle for considering a countable product instead (but still require
  knowledge of the round number).

@@

>>>>

\subtitle
{Spring Topology and Dynamics Conference 2015\\
Bowling Green State University} % (optional)

\author%[Author, Another] % (optional, use only with lots of authors)
{Steven~Clontz}%\inst{1} \and S.~Another\inst{2}}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\begin{document}
\renewcommand{\pause}{}
\newcommand{\vspacing}{\vspace{1em}}
\newcommand{\vpause}{\pause\vspacing}

@@

\section{Proximal Game}

@@

\begin{frame}
  If $\pl D\win \bellAbsConGame{X}$, then $X$ is called an
  \term{absolutely proximal space}.
  ``Absolutely proximal'' is a strengthening of ``proximal'' characterized
  by an easier game (for \(\pl D\)), but these games are equivalent for
  compact spaces.

@@

\section{Topological proximal game}

@@

  As it turns out, the union of all uniformities inducing a topology is
  itself a uniformity inducing that topology, called the
  \term{fine} or \term{universal uniformity}.
  Furthermore, $\pl D\win\bellAbsConGame{X}$
  if and only if $\pl D$ is required to choose from the universal uniformity.

@@

\begin{frame}
  If you look in the right textbook \cite{MR2048350}, you'll
  find the answer:

  \begin{theorem}
    A neighborhood $U$ of the diagonal is a universal entourage if
    and only if there
    exist neighborhoods $U_n$ for $n<\omega$ where $U=U_0$ and
    $U_{n+1}\circ U_{n+1}\subseteq U_n$.
  \end{theorem}

@@

  As a bonus, for paracompact spaces, \textit{all} neighborhoods of
  the diagonal have this property (entourages may be converted to open
  covers and then star-refined).

@@

  So we topologize Bell's game by simply calling the open symmetric
  neighborhoods of the diagonal with the above property ``entourages'',
  and discard the need to consider a specific uniform structure.
\end{frame}

@@

  \vpause
  A \term{$k$-Markov strategy} only uses the last $k$
  previous moves of the opponent and the round number.
  ($\pl A\kmarkwin{k} G$)

@@

\begin{frame}\small
  Bell observed that a winning perfect information strategy may always
  be passed down to win in a closed subspace.

@@

  This also holds for limited information strategies:

@@

\begin{frame}
  If we allow ourselves the round number, we may at least handle countable
  products:

@@

\begin{frame}
  A neat corollary:

  \begin{itemize}
  \item For compact spaces, \(\pl O\win\gruConGame{X^2}{\Delta}\) if and only
  if \(\pl D\win\bellAbsConGame{X}\).
  \end{itemize}

  but:

  \begin{itemize}
  \item Any metric space satisfies \(\pl O\tactwin\gruConGame{X^2}{\Delta}\),
  but \(\pl D\tactwin\bellAbsConGame{X}\) implies zero-dimensionality for
  compact spaces.
  \end{itemize}
\end{frame}
